An Inception Cohort Study Quantifying How Many Registered Studies are Published.

### 2023-05-29 paper.tex
incoporating comments Eline

Scientists selectively publish studies they perform (\protect\hyperlink{ref-franco_publication_2014}{Franco, Malhotra, \& Simonovits, 2014}; \protect\hyperlink{ref-greenwald_consequences_1975}{Greenwald, 1975}; \protect\hyperlink{ref-sterling_publication_1959}{Sterling, 1959}). Studies remain unpublished for a variety of reasons, such as a lack of resources to analyse the results, a loss of interest, perceived methodological weaknesses, or because the results do not support predictions (\protect\hyperlink{ref-easterbrook_publication_1991}{Easterbrook, Berlin, Gopalan, \& Matthews, 1991}; \protect\hyperlink{ref-lishner_sorting_2021}{Lishner, 2021}). Research resources are wasted when studies that have the potential to contribute to scientific knowledge go unpublished, (\protect\hyperlink{ref-buxton_avoiding_2021}{Buxton et al., 2021}; \protect\hyperlink{ref-chalmers_avoidable_2009}{Chalmers \& Glasziou, 2009}).

The practice of selective publication has been demonstrated in various disciplines, ranging from psychology and sociology to economics (\protect\hyperlink{ref-franco_publication_2014}{Franco et al., 2014}; \protect\hyperlink{ref-gerber_publication_2010}{Gerber, Malhotra, Dowling, \& Doherty, 2010}; \protect\hyperlink{ref-scheel_excess_2021}{Scheel, Schijen, \& Lakens, 2021}). It is challenging to quantify how many studies remain unpublished. The most accurate estimates come from inception cohort studies where studies are -- typically retroactively - followed from the moment they are started (\protect\hyperlink{ref-song_dissemination_2010}{Song et al., 2010}). Dickersin and colleagues observed that from all 737 studies submitted to two John Hopkins institutional review boards of the school of medicine and the school of health respectively 81\% and 66\% were published (\protect\hyperlink{ref-dickersin_factors_1992}{Dickersin, Min, \& Meinert, 1992}). Publication bias was mainly caused by researchers not submitting non-significant results, as only 6 out of 124 non-significant results submitted for publication were rejected by a journal. Of 293 clinical trials funded by NIH in 1979 93\% was published after a decade (\protect\hyperlink{ref-dickersin_nih_1993}{Dickersin \& Min, 1993}). In the only inception cohort study in the social sciences we know of, Franco et al.~(2014) found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45\%), 29\% of studies were written up but remained unpublished at the time of the study, and 20\% (primarily non-significant results) were unpublished and not written up.

@@

In this project we aimed to answer four main research questions. First, we were interested in estimating the number of registered studies on the OSF that were performed but remained unpublished after four years. Although this population of studies is not representative of all studies researchers perform (see the discussion), it is more representative of the studies researchers perform than the study by Franco and colleagues (2014) as any researcher can register a study on the OSF.

Second, we were interested in whether a registry with the policy to make registration public after an embargo facilitates identifying unpublished studies. By examining the publication status of registrations manually made public by researchers with registrations automatically opened by the OSF after four years we can estimate how researchers voluntarily share that they have collected data, even when the study remains unpublished, and how often a policy to automatically make a registration public makes performed but unpublished studies findable. This comparison can provide insights into the benefits of a platform that makes registrations public after a certain time, compared to platforms that permanently keep registrations private (e.g., AsPredicted.org).

Our third question concerns the possibility to correctly identify whether the study related to a registration is publicly shared, or not. For a registry to notify the scientific community about the presence of unpublished studies, the information in the registry needs to be complete enough to identify relevant studies and contact the researchers who performed the study. As far as we know, this is the first investigation that retrieves registrations from the OSF to attempt to identify whether the associated study has been publicly shared or not.
Finally, while it is useful to quantify how many registered studies remain unpublished after four years, it is also important to understand why studies remain unpublished. The fourth aim of our study was to contacted the researchers of registrations of studies that were not publicly shared and ask them whether the study indeed remained unpublished, and if so, why their study remained unpublished.

@@

\emph{Data sources}: As registrations become public after four years, we downloaded information about 17.729 registrations created on the OSF before November 18, 2017 (four years before the start of this study) through its application programming interface (API). Registrations are part of at least one associated project page on the OSF. Researchers might still work on projects four years after a registration. The final classification was based on whether the projects were public in April 2022. For 8008 registrations (45.17\%) the associated project was public, while for the remaining 9721 registrations (54.83\%) the associated project is private. We sampled registrations from both these groups. During data analysis we made sure that we did not include the same study twice (even though a single study can have multiple registrations, for example because an analysis subcomponent and a hypothesis subcomponent each get a separate ID in the OSF database). Our sampling strategy means that a study with multiple registrations is more likely to be included in our final sample.

@@

\emph{Inclusion criteria}: After some projects were reclassified during the data analysis in total 315 randomly chosen registrations from both groups were examined to see whether they met the selection criteria of our study. Of these, the associated project was public for 164 registrations and the associated project was closed for 151 registrations. As we are interested in estimating how many studies that were performed with the goal to publish the findings remain unpublished, registrations needed to be actual research studies where the goal of the researchers was to publish a paper. We therefore aimed to remove all registrations that were performed for practice purposes (e.g.~student assignments or trial registrations), as well as all registrations that were created to archive materials after the research project was completed (e.g., some journals ask researchers to use the registration option on the OSF to create a DOI that is linked to all files associated with the project after the manuscript has been accepted for publication). Furthermore, we excluded Registered Reports, as this publication format is much less susceptible to publication bias (\protect\hyperlink{ref-allen_open_2019}{Allen \& Mehler, 2019}; \protect\hyperlink{ref-chambers_past_2022}{Chambers \& Tzavella, 2022}; \protect\hyperlink{ref-scheel_excess_2021}{Scheel et al., 2021}). For each registration we coded whether they were (1) withdrawn, (2) a research study, (3) part of a multi-study project (i.e., the Reproducibility Project: Psychology), (4) a registration that occurred at the inception of the research project (i.e., not upon publication to generate a stable DOI for supplementary materials), and (5) a registered report.

The number of included and excluded registrations in the sample is summarized in Table \ref{tab:table-included}. We originally included 176 registrations. After excluding 7 registrations based on email responses for being student projects, or being performed without the goal of publishing the data, our final sample size consists of 169 registrations, where for 88 registrations the main project was public and for 81 registrations the main project was not public. An overview of how often registrations were excluded for each of the 5 inclusion criteria is provided in Table \ref{tab:table-excluded}.

@@

\begin{tabular}{lll}
\toprule
 & \multicolumn{1}{c}{Manually Opened (n = 164)} & \multicolumn{1}{c}{Automatically Opened (n = 151)}\\
\midrule
Included Before Emails & 90 & 86\\
Percentage Before Emails & 55 & 57\\
Included After Emails & 88 & 81\\
Percentage After Emails & 54 & 54\\
Total & 164 & 151\\
\bottomrule
\addlinespace
\end{tabular}

@@

\begin{tabular}{lll}
\toprule
 & \multicolumn{1}{c}{Manually Opened} & \multicolumn{1}{c}{Automatically Opened}\\
\midrule
Withdrawn & 1 & 5\\
No Research Study & 21 & 50\\
No Unique Study & 13 & 5\\
No Registration & 27 & 20\\
Registered Report & 13 & 3\\
Replication Project & 12 & 1\\
\bottomrule
\end{tabular}

@@

For all registrations where we were uncertain about whether a publication corresponded to the registration, we attempted to retrieve contact information of researchers involved, and contacted the researchers. We also contacted researchers associated with all registrations classified after an extensive search as unpublished, to check if the registration was indeed unpublished, and if so, ask the researchers why the study remained unpublished. We contacted 109 researchers, 29 researchers with registrations associated with public OSF projects and 80 researchers with registrations associated with closed OSF projects, of which 24 (82.76\%) and 53 (66.25\%) replied to our email with additional information to update our classification. We sent 1 email for a registration classified as published because we found a thesis in a repository to check if a paper had been published (and received 1 response), for one registration we did not have to email the researcher because we could retrieve the required information from a paper in which they explicitly discussed their file-drawer (\protect\hyperlink{ref-van_elk_whats_2021}{van Elk, 2021}), 77 emails for registrations we believed remained unpublished (and received 51 responses), and 31 emails because we were uncertain if they were published or not (and received 25 responses). Two additional researchers replied to our email, but did not give consent to use their replies in our data analysis, and we therefore did not change the classification of these two registrations.

After updating our classification based on email responses, the publication rate in group 1 increased by 6\% (meaning that we failed to identify some publications corresponding to registrations) while the publication rate in group 2 decreased by 1\%. Sometimes a publication we found in the literature did not belong to the registration. If the study associated with the registration was published in another source than the one we identified, the classification remained the same, but we still counted this registration as a mismatch because we failed to identify the correct article without the help of the researchers. In total, 48 of the 76 responses match with publications we found. For the 50 registrations we classified as unpublished, responses to the follow-up emails indicated that 36 (72\%) were unpublished, while for 14 (28\%) we failed to identify the published paper based on the information in the registration. We received 25 responses for registrations we were uncertain about, and these follow-up emails indicated that 11 (44\%) were unpublished, while for 14 (28\%) we failed to identify the published paper based on the information in the registration.

Most of the mismatches occurred when we were uncertain about whether a paper we found included the registered study because there was no link to the registration on the OSF and only some terminology in the registration and article overlapped. For the 25 registrations where we were uncertain if the study was published, 11 (44\%) of registrations matched a paper we found. Of the 14 cases in this group that were a mismatch, 2 were indeed published but we failed to find the correct paper, and the remaining 12 were actually not published. In one special case the paper we found was indeed a match, but we decided to change the final classification to unpublished as the registration belonged to two studies and only one of the registered studies was published. Altogether, these results indicate that without contacting the researchers it is difficult to categorize studies as published or unpublished based exclusively on the information researchers provide in their registration on the OSF.

Due to non-response to our emails there is remaining uncertainty about the number of registrations in our sample that were eventually published. The 26 non-responses related to registrations where we could not find a publication might contain some publications that we missed, and the 6 non-responses related to registrations where we remained uncertain similarly contain some published studies. Researchers might be more likely to reply when their registration is actually published, or non-response might be unaffected by the publication status of their registration. Under the latter assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that 19.45 out of 26 of the registration in the unpublished classification and 3.03 out of 6 of the registration in the uncertain classification are actually published.

@@

After incorporating responses from researchers, and extrapolating these responses to the registrations where we did not receive a response, we predict that out of a total of 169 included registrations, 103.52 registered studies are published (61.25\%, 95\% CI {[}53.74; 68.27{]}). Our sample intentionally contained an almost equal number of manually opened and automatically opened registrations. As can be seen in Table \ref{tab:table-estimated-nonpublication} manually opened registrations were much more likely to be published than automatically opened registrations, but also somewhat less frequent in the total population of registrations. Multiplying our publication estimates by the estimated number of research studies registered on the OSF before November 2017 we see that 5550 registrations are published, and 3994 remain unpublished. Therefore, in the total population of all registrations on the OSF from before November 2017 we estimated that 58.15\%, of registrations are published as an article, preprint, thesis, or poster after at least four years.

@@

We see that 85.91\%, 95\% CI {[}77.13; 91.68{]} of all registrations that based on our proxy were classified as manually opened by the researchers have been published. In the remaining 14.09\% of these registrations researchers have voluntarily chosen to make the registration public, even though the study was not published. This shows that a platform that enables researchers to make their registration public will make studies that would otherwise remain in the file-drawer known to the research community. We estimate that 34.47\%, 95\% CI {[}25.04; 45.31{]} of automatically opened registrations is published. Consequently, 65.53\% of these registrations would not be known to the research community were it not for the fact that the OSF automatically opens registrations after four years. In other words, automatically opening registrations increases our awareness of all studies have been performed, above and beyond enabling researchers to create public registrations that they can voluntarily make public.

@@

There can be many reasons why a researcher does not publish a performed study. We classified the responses given by researchers into 5 categories (see Table \ref{tab:table-reasons}, for a more detailed overview, see the online supplement). Researchers indicated their motivation to not publish were based on (1) the results of the study, such as null or unclear results and failed replications (25\%), (2) the review process, such as that the paper was rejected, or that reviewers thought it would be better to leave this study out (27\%), (3) the goal of the study, which was not publishing the results because the project was educational or intended to be shared with stakeholders (4\%), (4) planning, such as a lack of time, or a new job on a different research topic or outside of academia (45\%), and (5) problems with the study design (5\%).

@@

When asked why researchers made their OSF project page open, most researchers (2 out of 23 mentioned a motivation to practice open science. Out of 43 responses more diverse reasons were given for keeping the OSF project closed, such as that there was no relevant information there (15 times), researchers forgot to open it (11 times), waiting until a project was published (6 times), and technical issues (4 times). For more details, see the online supplement. Finally, we were interested in how many researchers who registered on the OSF before 2017 - many of which should be considered early adopters - were aware of the OSF policy to automatically open all registrations after four years. Although not all of the email respondents answered this question, 24 of the researchers indicated they were aware of this policy, and 14 were not aware of this policy.

@@

Our examination of 169 registrations led to an estimated publication rate of 58.15\%, for all registrations on the Open Science framework that were created before November 18, 2017. Extrapolating from our sample, we estimate that of the 9544 registered research studies on the OSF that met our inclusion criteria, 3994 remain unpublished. The main reason researchers give when asked why their studies remain unpublished are logistical issues related to a lack of time, or responsible researchers moving on to a new job. Our study provides an important datapoint to understand how many studies are performed, but never shared. The possibility that around 41.85\% of research studies registered on the OSF are not shared should make scientists reflect on the efficiency of scientific research. Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced (\protect\hyperlink{ref-bernal_social_1939}{Bernal, 1939}; \protect\hyperlink{ref-chalmers_avoidable_2009}{Chalmers \& Glasziou, 2009}), wherever this waste is avoidable.

The fact that for 20\% of unpublished studies researchers indicated that the reason that the study remained unpublished ia due to the results (e.g., null results or failed replications) is concerning. It is possible that the absence of these studies contributes to publication bias in the scientific literature. Researchers can prevent the results of a study from influencing the probability that their study will be published by submitting their registration as a Registered Report (\protect\hyperlink{ref-chambers_past_2022}{Chambers \& Tzavella, 2022}; \protect\hyperlink{ref-nosek_registered_2014}{Nosek \& Lakens, 2014}). Compared to the standard literature, where almost all studies support their hypotheses, Registered Reports are much more likely to report null results (\protect\hyperlink{ref-allen_open_2019}{Allen \& Mehler, 2019}; \protect\hyperlink{ref-scheel_excess_2021}{Scheel et al., 2021}). If researchers do not report failed replications it is impossible to correct false positive claims in the scientific literature, and if null-results remain unreported effect size estimates in meta-analyses will be inflated to an extent. With the rise of data repositories and preprints it has become feasible and easy to share the results of studies, although future work that makes it easier to find, evaluate, and integrate study results is important.

It is important to keep in mind that our estimate of the number of registrations on the OSF that are published after four years has 1) remaining uncertainty, and 2) is unlikely to generalize beyond the specific context of our study. First, even after contacting researchers, due to non-response some registrations will be classified incorrectly, and the true number of unpublished studies in our sample could differ slightly from the numbers we report. Second, the estimate is specific to the context of our study, which were all registrations on the Open Science Framework created before November 18, 2017. The practice to register studies is becoming more widespread, but up to 2017 was predominantly done by early adopters interested in open science practices. It is possible that this group of researchers differs in how likely they are to share studies they have performed compared to researchers who did not register in this time-window, for example because researchers who adopt open science practices early more actively aim to publish null results, or reduce the size of their file-drawer. We studied the probability that a registered study was published, which might differ from the probability that a non-registered study is published. Registering a study requires work, and it possible that researchers only register studies they feel have a higher probability of being submitted for publication. Because the practice of registering studies on the OSF up to 2017 was more widespread in experimental social psychology, it remains unknown how many studies remain unpublished in other disciplines. The probability that researchers have the time to share data from a registered study might change over time, and could for example be in recent years due to the COVID pandemic. In short, it is unclear whether our estimates generalize to different populations of scientists, different populations of studies, different disciplines, and whether this estimate remains stable over time.

However, our goal was not to establish a generalizable estimate. The variation in the percentage of unpublished studies across scientific contexts is undoubtedly large. At the same time, the factors that cause researchers to not publish results (e.g., a lack of time, responsible researchers leaving academia, null results, rejections during peer review) play a role in many (if not all) scientific contexts. Our study demonstrates that the percentage of unpublished studies can be high, and deserves attention across scientific contexts where similar factors preventing the publication of studies play a role. In fields where most studies are submitted as a Registered Report, researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and all studies are designed to have a high probability to yield informative results, there might be few unpublished studies. In fields where Registered Reports are rare, team science is less common, and less informative studies are designed, estimates of published results might be similar to those observed in our sample. Researchers who take efficient knowledge generation in their own scientific context seriously might want to empirically examine the question how many studies go unpublished to determine if there is room for improvement.

\emph{Recommendations for Registries}. We found that registrations are sometimes used to create a stable repository after a study has been completed, and sometimes to register the existence (and sometimes methodological details) of a planned study. To be able to distinguish these to uses of registries, it might be useful to create separate categories of registrations (e.g., distinguishing `prospective registration' or `preregistration' from `post registration' or `data archiving'). A third registration option should be created for all registrations that are done for purely educational or practice purposes. The content of these registrations could remain the same, but some features (such as the automatically created DOI) could be omitted to save money. It would be useful for meta-scientific research if the API that allows researchers to access data from the registry could distinguish different types of registrations (e.g., pre- and post-registrations), and if the API made it possible to retrieve whether a registration was made public manually, or automatically after 4 years. Lastly, the OSF currently displays registrations of separate components of the same project as unique registrations. It would be clearer if separate components belonging to the same registration would not be displayed as the same registrations. Alternatively, an extra field could be added that indicates that a registration is a sub-component of a certain larger project.

>>>>

Not all studies scientists perform end up in the scientific literature (\protect\hyperlink{ref-franco_publication_2014}{Franco, Malhotra, \& Simonovits, 2014}; \protect\hyperlink{ref-greenwald_consequences_1975}{Greenwald, 1975}; \protect\hyperlink{ref-sterling_publication_1959}{Sterling, 1959}). Studies remain unpublished for a variety of reasons, such as a lack of resources to analyse the results, a loss of interest, perceived methodological weaknesses, or because the results do not support predictions (\protect\hyperlink{ref-easterbrook_publication_1991}{Easterbrook, Berlin, Gopalan, \& Matthews, 1991}; \protect\hyperlink{ref-lishner_sorting_2021}{Lishner, 2021}). When studies that have the potential to contribute to scientific knowledge go unpublished, research resources are wasted (\protect\hyperlink{ref-buxton_avoiding_2021}{Buxton et al., 2021}; \protect\hyperlink{ref-chalmers_avoidable_2009}{Chalmers \& Glasziou, 2009}). The practice of selective publication has been demonstrated in various disciplines, such as psychology, sociology, economics, and medicine (\protect\hyperlink{ref-franco_publication_2014}{Franco et al., 2014}; \protect\hyperlink{ref-gerber_publication_2010}{Gerber, Malhotra, Dowling, \& Doherty, 2010}; \protect\hyperlink{ref-scheel_excess_2021}{Scheel, Schijen, \& Lakens, 2021}), but it is challenging to quantify how many studies remain unpublished, and are locked away in the proverbial file drawer (\protect\hyperlink{ref-rosenthal_file_1979}{Rosenthal, 1979}).

The most accurate estimates of the percentage of performed studies in the file drawer come from inception cohort studies where studies are -- typically retroactively - followed from the moment they are started (\protect\hyperlink{ref-song_dissemination_2010}{Song et al., 2010}). Dickersin and colleagues observed that from all 737 studies submitted to two John Hopkins institutional review boards of the school of medicine and the school of health respectively 81\% and 66\% were published (\protect\hyperlink{ref-dickersin_factors_1992}{Dickersin, Min, \& Meinert, 1992}). Publication bias was mainly caused by researchers not submitting non-significant results, as only 6 out of 124 non-significant results submitted for publication were rejected by a journal. Of 293 clinical trials funded by NIH in 1979 93\% was published after a decade (\protect\hyperlink{ref-dickersin_nih_1993}{Dickersin \& Min, 1993}). In the only inception cohort study in the social sciences we know of, Franco et al. (\protect\hyperlink{ref-franco_publication_2014}{2014}) found that out of 249 experiments 106 were published in a scientific journal or as a book chapter (45\%), 29\% of studies were written up but remained unpublished at the time of the study, and 20\% (primarily non-significant results) were unpublished and not written up.

@@

In this project we aimed to answer four main research questions. First, we were interested in estimating the number of registered studies on the OSF that were performed but remained unpublished after four years. Although this population of studies is not representative of all studies researchers perform (see the discussion), it is more representative of the studies researchers perform than the study by Franco and colleagues (\protect\hyperlink{ref-franco_publication_2014}{2014}) as any researcher can register a study on the OSF.

Second, we were interested in whether a registry with the policy to make registration public after an embargo facilitates identifying unpublished studies. By comparing the publication status of registrations manually made public by researchers with registrations automatically opened by the OSF after four years we can estimate how researchers voluntarily share that they have collected data, even when the study remains unpublished, and how often a policy to automatically make a registration public makes performed but unpublished studies findable. This comparison can provide insights into the benefits of a platform that makes registrations public after a certain time, compared to platforms that permanently keep registrations private (e.g., AsPredicted.org).

Our third question concerns the possibility to correctly identify whether a registered study is publicly shared, or not. For a registry to notify the scientific community about the presence of unpublished studies, the information in the registry needs to be complete enough to match the registration to a published study, or to conclude the registered study remains unpublished. As far as we know, this is the first investigation that retrieves registrations from the OSF to attempt to identify whether the associated study has been publicly shared or not.

Finally, while it is useful to quantify how many registered studies remain unpublished after four years, it is equally important to understand why studies remain unpublished. The fourth aim of our study was to contact researchers of registrations of studies that were not publicly shared and ask them whether the study indeed remained unpublished, and if so, ask why their study remains unpublished.

@@

\emph{Data sources}: As registrations become public after four years, we downloaded information about 17.729 registrations created on the OSF before November 18, 2017 (four years before the start of this study) through its application programming interface (API). Registrations are part of at least one associated project page on the OSF. Sometimes researchers still work on projects four years after a registration, and we saw continued activity in some registrations in our sample. The final classification was based on whether the projects were public in April 2022. For 8008 registrations (45.17\%) the associated project was public, while for the remaining 9721 registrations (54.83\%) the associated project is private. We sampled registrations from both these groups. During data analysis we made sure that we did not include the same study twice (even though a single study can have multiple registrations, for example because an analysis subcomponent and a hypothesis subcomponent each get a separate ID in the OSF database). Our sampling strategy means that a study with multiple registrations is more likely to be included in our final sample.

@@

\emph{Inclusion criteria}: After some projects were reclassified during the data analysis in total 315 randomly chosen registrations from both groups were examined to see whether they met the selection criteria of our study. Of these, the associated project was public for 164 registrations and the associated project was closed for 151 registrations. Registrations needed to be actual research studies, as we are interested in estimating how many studies remain unpublished when researchers had the goal to publish. We therefore coded and excluded registrations that were (1) withdrawn, (2) performed for practice purposes (e.g.~student assignments or trial registrations), (3) used to generate a stable DOI for supplementary materials at the end of a project, and studies that are much less susceptible to publication bias such as (4) Registered Reports, (\protect\hyperlink{ref-allen_open_2019}{Allen \& Mehler, 2019}; \protect\hyperlink{ref-chambers_past_2022}{Chambers \& Tzavella, 2022}; \protect\hyperlink{ref-scheel_excess_2021}{Scheel et al., 2021}), and (5) multi-lab projects (i.e., the Reproducibility Project: Psychology).

The number of included and excluded registrations in the sample is summarized in Table \ref{tab:table-included}. We originally included 176 registrations. After excluding 7 registrations based on email responses for being student projects, performed without the goal of publishing the data, or part of a multi-lab project, our final sample size consists of 169 registrations, where for 88 registrations the main project was public and for 81 registrations the main project was not public. An overview of how often registrations were excluded for each of the 5 inclusion criteria is provided in Table \ref{tab:table-excluded}.

@@

\begin{tabular}{lll}
\toprule
 & \multicolumn{1}{c}{Included Before Emails} & \multicolumn{1}{c}{Included After Emails}\\
\midrule
Manually Opened (n = 164) & 90 (54.88\%) & 88 (53.66\%)\\
Automatically Opened (n = 151) & 86 (56.95\%) & 81 (53.64\%)\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lll}
\toprule
 & \multicolumn{1}{c}{Manually Opened} & \multicolumn{1}{c}{Automatically Opened}\\
\midrule
Withdrawn & 1 & 5\\
No Research Study & 21 & 50\\
No Unique Study & 13 & 5\\
No Registration & 27 & 20\\
Registered Report & 13 & 3\\
Replication Project & 12 & 1\\
\bottomrule
\addlinespace
\end{tabular}

@@

For all registrations where we were uncertain about whether a publication corresponded to the registration, we attempted to retrieve contact information of researchers involved, and contacted the researchers. We also contacted researchers associated with all registrations classified after an extensive search as unpublished, to check if the registration was indeed unpublished, and if so, ask the researchers why the study remained unpublished. We contacted 109 researchers, 29 researchers with registrations associated with public OSF projects and 80 researchers with registrations associated with closed OSF projects, of which 24 (82.76\%) and 53 (66.25\%) replied to our email with additional information to update our classification. We sent one email for a registration classified as published because we found a thesis in a repository to check if a paper had been published (and received one response), for one registration we did not have to email the researcher because we could retrieve the required information from a paper in which they explicitly discussed their file-drawer (\protect\hyperlink{ref-van_elk_whats_2021}{van Elk, 2021}), 77 emails for registrations we believed remained unpublished (and received 51 responses), and 31 emails because we were uncertain if they were published or not (and received 25 responses). Two additional researchers replied to our email, but did not give consent to use their replies in our data analysis, and we therefore did not change the classification of these two registrations.

After updating our classification based on email responses, the publication rate in group 1 increased by 6\% (meaning that we failed to identify some publications corresponding to registrations) while the publication rate in group 2 decreased by 1\%. Sometimes a publication we found in the literature did not belong to the registration. If the study associated with the registration was published in another source than the one we identified, the classification remained the same, but we still counted this registration as a mismatch because we failed to identify the correct article without the help of the researchers. In total, 48 of the 76 responses match with publications we found. For the 50 registrations we classified as unpublished, responses to the follow-up emails indicated that 36 (72\%) were unpublished, while for 14 (28\%) we failed to identify the published paper based on the information in the registration. Most of the mismatches occurred when we were uncertain about whether a paper we found included the registered study because there was no link to the registration on the OSF and only some terminology in the registration and article overlapped. For the 25 registrations where we were uncertain if the study was published, 11 (44\%) of registrations matched a paper we found. Of the 14 (28\%) cases in this group that were a mismatch, 2 were indeed published but we failed to find the correct paper, and the remaining 12 were actually not published. In one special case the paper we found was indeed a match, but we decided to change the final classification to unpublished as the registration belonged to two studies and only one of the registered studies was published. Altogether, these results indicate that without contacting the researchers it is often difficult to determine whether a registration is published based exclusively on the information researchers provide in their registration on the OSF.

Due to non-response to our emails there is remaining uncertainty about the number of registrations in our sample that were eventually published. The 26 non-responses related to registrations where we could not find a publication might contain some publications that we missed, and the 6 non-responses related to registrations where we remained uncertain similarly contain some published and some unpublished studies. Researchers might be more likely to reply when their registration is actually published, or non-response might be unaffected by the publication status of their registration. Under the latter assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that 19.45 out of 26 of the registration in the unpublished classification and 3.03 out of 6 of the registration in the uncertain classification are actually published.

@@

After incorporating responses from researchers, and extrapolating these responses to the registrations where we did not receive a response, we predict that out of a total of 169 included registrations, 103.52 registered studies are published (61.25\%, 95\% CI {[}53.74; 68.27{]}). Our sample intentionally contained an almost equal number of manually opened and automatically opened registrations. As can be seen in Table \ref{tab:table-estimated-nonpublication} manually opened registrations were much more likely to be published than automatically opened registrations, but also somewhat less frequent in the total population of registrations. Multiplying our publication estimates by the estimated number registrations on the OSF before November 2017 that can be classified as an actual research study we find that 5550 registrations are published, and 3994 remain unpublished. Therefore, in the total population of all registrations on the OSF from before November 2017 we estimated that 58.15\%, of registrations are published as an article, preprint, thesis, or poster after at least four years.

@@

We see that 85.91\%, 95\% CI {[}77.13; 91.68{]} of all registrations that based on our proxy were classified as manually opened by the researchers have been published. In the remaining 14.09\% of these registrations researchers have voluntarily chosen to make the registration public, even though the study was not published. This shows that a platform that enables researchers to make their registration public will make studies that would otherwise remain in the file-drawer known to the research community. We estimate that 34.47\%, 95\% CI {[}25.04; 45.31{]} of automatically opened registrations is published. Consequently, 65.53\% of these registrations would not be known to the research community were it not for the fact that the OSF automatically opens registrations after four years. In other words, automatically opening registrations increases our awareness of all studies that have been performed, above and beyond enabling researchers to create public registrations that they can voluntarily make public.

@@

There can be many reasons why a researcher does not publish a performed study. We classified the responses given by researchers into 5 categories (see Table \ref{tab:table-reasons}, for a more detailed overview, see the online supplement). Researchers indicated that their motivation to not publish was based on (1) the results of the study, such as null or unclear results and failed replications (25\%), (2) the review process, such as that the paper was rejected, or that reviewers thought it would be better to leave this study out (27\%), (3) the goal of the study, which was not publishing the results because the project was educational or intended to be shared with stakeholders (4\%), (4) planning, such as a lack of time, or a new job on a different research topic or outside of academia (45\%), and (5) problems with the study design (5\%).

@@

When asked why researchers made their OSF project page open, most researchers (18 out of 23) mentioned a motivation to practice open science. Out of 43 responses more diverse reasons were given for keeping the OSF project closed, such as that there was no relevant information stored in the project (15 times), researchers forgot to open it (11 times), were waiting until a project was published (6 times), or experienced technical issues (4 times). For more details, see the online supplement. Finally, we were interested in how many researchers who registered on the OSF before 2017 - many of which should be considered early adopters - were aware of the OSF policy to automatically open all registrations after four years. Although not all of the email respondents answered this question, 24 of the researchers indicated they were aware of this policy, and 14 were not aware of this policy.

@@

Our examination of 169 registrations led to an estimated publication rate of 58.15\%, for all registrations on the Open Science framework that were created before November 18, 2017. Extrapolating from our sample, we estimate that of the 9544 registered research studies on the OSF that met our inclusion criteria, 3994 remain unpublished. The main reason researchers give when asked why their studies remain unpublished are logistical issues related to a lack of time, or responsible researchers moving on to a new job. Our study provides an important datapoint to understand how many studies are performed, but never shared. The possibility that around 41.85\% of research studies registered on the OSF (excluding multi-lab studies and Registered Reports) are not shared should make scientists reflect on the efficiency of scientific research. Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced (\protect\hyperlink{ref-bernal_social_1939}{Bernal, 1939}; \protect\hyperlink{ref-chalmers_avoidable_2009}{Chalmers \& Glasziou, 2009}), wherever this waste is avoidable.

The fact that for 20\% of unpublished studies researchers indicated that the reason that the study remained unpublished is due to the results (e.g., null results or failed replications) is concerning, and considered unacceptable by the general public (\protect\hyperlink{ref-bottesini_what_2022}{Bottesini, Rhemtulla, \& Vazire, 2022}; \protect\hyperlink{ref-pickett_questionable_2017}{Pickett \& Roche, 2017}). It is possible that the absence of these studies contributes to publication bias in the scientific literature. Researchers can prevent the results of a study from influencing the probability that their study will be published by submitting their registration as a Registered Report (\protect\hyperlink{ref-chambers_past_2022}{Chambers \& Tzavella, 2022}; \protect\hyperlink{ref-nosek_registered_2014}{Nosek \& Lakens, 2014}). Compared to the standard literature, where almost all studies support their hypotheses, Registered Reports are much more likely to report null results (\protect\hyperlink{ref-allen_open_2019}{Allen \& Mehler, 2019}; \protect\hyperlink{ref-scheel_excess_2021}{Scheel et al., 2021}). If researchers do not report failed replications it is impossible to correct false positive claims in the scientific literature, and if null-results remain unreported effect size estimates in meta-analyses will be inflated to an extent. With the rise of data repositories and preprints it has become feasible and easy to share the results of studies.

It is important to keep in mind that our estimate of the number of registrations on the OSF that are published after four years has 1) remaining uncertainty, and 2) is unlikely to generalize beyond the specific context of our study. First, even after contacting researchers, due to non-response some registrations will be classified incorrectly, and the true number of unpublished studies in our sample could differ slightly from the numbers we report. Second, the estimate is specific to the context of our study, which were all registrations on the Open Science Framework created before November 18, 2017. Users of the OSF in these years are early adopters interested in open science practices. It is possible that this group of researchers differs in how likely they are to share studies they have performed compared to researchers who did not register in this time-window, for example because researchers who adopt open science practices early more actively aim to publish null results, or reduce the size of their file-drawer. We studied the probability that a registered study was published, which might differ from the probability that a non-registered study is published. Registering a study requires work, and it is possible that researchers only register studies they feel have a higher probability of being submitted for publication. Because the practice of registering studies on the OSF up to 2017 was more widespread in experimental social psychology, it remains unknown how many studies remain unpublished in other disciplines. The probability that researchers have the time to share data from a registered study might change over time, and could be higher due to the COVID pandemic. In short, it is unclear whether our estimates generalize to different populations of scientists, different populations of studies, different disciplines, and whether this estimate remains stable over time.

However, our goal was not to establish a generalizable estimate. The variation in the percentage of unpublished studies across scientific contexts is undoubtedly large. At the same time, the factors that cause researchers to not publish results (e.g., a lack of time, responsible researchers leaving academia, null results, rejections during peer review) play a role in many (if not all) scientific contexts. Our study demonstrates that the percentage of unpublished studies can be high, and deserves attention across scientific contexts where similar factors preventing the publication of studies play a role. In fields where most studies are submitted as a Registered Report, researchers work in larger teams where one team member takes over the work of a colleague who leaves academia, and all studies are designed to have a high probability to yield informative results, so there might be few unpublished studies. In fields where Registered Reports are rare, team science is less common, and less informative studies are designed, estimates of published results might be similar to those observed in our sample. Researchers who take efficient knowledge generation in their own scientific context seriously might want to empirically examine the question how many studies go unpublished to determine if there is room for improvement.

\emph{Recommendations for Registries}. We found that registrations are not only used to register a study, but also to create a stable archive after a study has been completed. To be able to distinguish these uses of registries, it might be useful to create separate categories of registrations (e.g., distinguishing `prospective registration' or `preregistration' from `post registration' or `data archiving'). A third registration option should be created for all registrations that are done for purely educational or practice purposes. The content of these registrations could remain the same, but some features (such as the automatically created DOI) could be omitted to save money. It would be useful for meta-scientific research if the API that allows researchers to access data from the registry could distinguish different types of registrations (e.g., pre- and post-registrations), and if the API made it possible to retrieve whether a registration was made public manually, or automatically after 4 years. Lastly, the OSF currently displays registrations of separate components of the same project as unique registrations. It would be clearer if separate components belonging to the same registration would not be displayed as the same registrations. Alternatively, an extra field could be added that indicates that a registration is a sub-component of a certain larger project.
